Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-10-22 SupportingInformation.Rmd
fixing tables

---
title: "Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields"
author: "S. Ghosh, T. Loecke, C.P. Reid, D.C. Reuman"
date: "February 12, 2018"
geometry: "left=1cm,right=1cm,top=2.5cm,bottom=2.8cm"

@@

<!--The raw data look like this:-->
```{r load_data_Loecke, echo=F, results='hide'}
#fig.cap="Plot of the raw soil C and N data.\\label{fig_raw_cop_soilCN}(A)", fig.height=3, fig.width=3}
d<-readRDS("Data/RaCA_soilorganicC_soiltotalN_stocks100cm.RDS")
d<-d[,c("SOCstock100","TSNstock100")]
pdf("./Results/SoilCNraw.pdf")
op<-par(mar=c(5.1, 4.1, 0.2, 2.1))
plot(d[,1],d[,2],type="p",col="red",xlab="Soil C",ylab="Soil N",cex.lab=1.5,cex.axis=1.5)
par(op)
dev.off()
```

@@

b<-log10(raw_b)
colnames(b)<-c("log10M(g)","log10BMR(KJ/h)")
pdf("./Results/BMR_results/birds/raw_birds_BMR.pdf")
op<-par(mar=c(5.1, 4.1, 0.2, 2.1))
plot(b[,1],b[,2],type="p",col="red",xlab="log(Mass)",ylab="log(BMR)",cex.lab=1.5,cex.axis=1.5)
par(op)
dev.off()

@@

pdf("./Results/BMR_results/mammals/raw_mammals_BMR.pdf")
op<-par(mar=c(5.1, 4.1, 0.2, 2.1))
plot(m[,1],m[,2],type="p",col="red",xlab="log(Mass)",ylab="log(BMR)",cex.lab=1.5,cex.axis=1.5)
par(op)
dev.off()

@@

  if(ploton==T){
    if(rawplot==T){
      op<-par(mar=c(5.1, 4.1, 1.5, 2.1))
      plot(tab_dbp$avg.H,tab_dbp$avg.Biomass,xlab="avg.H",ylab="avg.Biomass",col="red",pch=1,cex.lab=1.6,cex.axis=1.5)
      mtext(paste0("Year=",year),cex=1.5)
      par(op)
    }else{
      op<-par(mar=c(5.1, 4.1, 1.5, 2.1))
      plot(cop_tab_dbp$avg.H,cop_tab_dbp$avg.Biomass,xlab="u",ylab="v",col="red",pch=1,cex.lab=2,cex.axis=1.5,
         xlim=c(0,1),ylim=c(0,1),asp=1)
      rect(0,0,1,1)
      lines(c(0,1),c(0,1),type='l')
      mtext(paste0("Year=",year),cex=1.5)
      par(op)
    }
  }

@@

@@

\newpage
<!--Display model selection results for BMR:birds data in a table-->
```{r tab_bmr_mammals_fit, echo=F, results='markup'}
h<-BivMS_mammals$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
knitr::kable(h,
             format='pandoc',
             caption = "Fitting info for **mammals' BMR dataset** . \\label{tab_bmr_mammals_fit}",
             booktabs=T)
```

@@

```{r tab_count_bestcop, echo=F, results="markup"}
#library(dplyr)
#knitr::opts_knit$set(kable.force.latex = TRUE)
knitr::kable(RES_aphid_count$info_ord_copname[,,1], #longtable = T,
             format='pandoc',
             #caption.short = "Best-fitting copulas for each location pair from among those considered, according to AIC, for abundances of the green spruce aphid.",
             caption = "Best-fitting copulas for each location pair from among those considered, according to AIC, for **abundances of the green spruce aphid**. Copulas 
considered were the normal, Clayton, Gumbel, Frank, Joe, BB1, BB6, BB7, BB8, survival Clayton, survival Gumbel, 
survival Joe, survival BB1, survival BB6, survival BB7, survival BB8 copulas. Abbreviations were given in \\nameref{MT-Methods}. NA occurs along the diagonal of the matrix because the diagonal represents a sampling location compared to itself.\\label{tab_count_bestcop}",
             booktabs=TRUE
             )#%>% # only with 'latex'/'html' format
 # kableExtra::kable_styling(latex_options = c("striped","HOLD_position"))
```

@@

\newpage
```{r tab_count_AICw_normal, echo=F, results='markup'}
source("normal_cop_AICw.R")
knitr::kable(normal_cop_AICw_matrix(r=RES_aphid_count),
             format='pandoc',
             caption = "$\\text{AIC}_{\\text{w}}$ for the normal copula family for each location pair for **abundances of the green spruce aphid**, for comparison with Table \\ref{tab_count_AICw}. \\label{tab_count_AICw_normal}",
             booktabs=TRUE
             )
```

@@

```{r tab_count_LTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_count$LTdep_AICw,
             format='pandoc',
             caption = "Model-averaged lower tail dependence statistic for each location pair for **abundances of the green spruce aphid**.\\label{tab_count_LTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_count_UTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_count$UTdep_AICw,
             format='pandoc',
             caption = "Model averaged upper tail dependence statistic for each location pair for **abundances of the green spruce aphid**.\\label{tab_count_UTdep_AICw}",
             booktabs=TRUE
             )
```

```{r tab_count_LTmUT, echo=F, results='markup'}
knitr::kable(RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw,
             digits = 5,
             format='pandoc',
             caption = "Model averaged lower tail dependence minus model averaged upper tail dependence statistic for each location pair for **abundances of the green spruce aphid**.\\label{tab_count_LTmUT}",
             booktabs=TRUE
             )
```

@@

```{r tab_ff_AICw_normal, echo=F, results='markup'}
source("normal_cop_AICw.R")
knitr::kable(normal_cop_AICw_matrix(r=RES_aphid_ff),
             format='pandoc',
             caption = "$\\text{AIC}_{\\text{w}}$ for the normal copula family for each location pair for **first flight data for the leaf-curlung plum aphid**, for comparison with Table \\ref{tab_ff_AICw}.\\label{tab_ff_AICw_normal}",
             booktabs=TRUE
             )
```

@@

<!--display the main statistical results in a table-->
```{r tab_methane_resamp,echo=F,results="markup"}
s<-stat_methane$numericdf[,c(3,2,4)]
colnames(s)<-c("Lower 95\\% CI", "Mean", "Upper 95\\% CI")
rownames(s)<-c("Spearman","Kendall","$\\cor_l$","$\\cor_u$","$\\Ps_l$","$\\Ps_u$","$\\Dsq_l$","$\\Dsq_u$","$\\cor_l - \\cor_u$","$\\Ps_l - \\Ps_u$","$\\Dsq_u - \\Dsq_l$")
knitr::kable(s,
             format = "pandoc",
             caption = "Spatially averaged values of statistics and confidence intervals based on resampling for **methane-flux data**.\\label{tab_methane_resamp}",
             booktabs=TRUE)
```

@@

  d<-dim(r$gfc_numBS)[1]
  m$num.pairs<-(d^2)-d 
  m$`num.non-indep`<- (d^2)-d-2*(r$num_indep_loc_pair+r$num_neg_cor_loc_pair)
  m$`num.non-N`<-sum(r$info_ord_copcode[,,1]!=1,na.rm = T)
  r$info_ord_AICw[r$info_ord_AICw==Inf] <- NaN
  m$Avg.best.AICw<-round(mean(r$info_ord_AICw[,,1],na.rm = T),3)
  normal_AICw[normal_AICw==Inf]<-NaN
  m$Avg.N.AICw<-round(mean(normal_AICw,na.rm=T),3)
  temp<-which((r$gfc_p_CvM>0.01) & (r$gfc_p_KS>0.01),arr.ind=T)
  m$num.good.fit<-dim(temp)[1]
  t<-r$LTdep_AICw[is.finite(r$LTdep_AICw)]
  CI_LT<-unname(quantile(t,probs=c(0.025,0.975),na.rm = T))
  m$`0.025-CI.LT`<-round(CI_LT[1],3)
  m$`0.975-CI.LT`<-round(CI_LT[2],3)
  t<-r$UTdep_AICw[is.finite(r$UTdep_AICw)]
  CI_UT<-unname(quantile(t,probs=c(0.025,0.975),na.rm = T))
  m$`0.025-CI.UT`<-round(CI_UT[1],3)
  m$`0.975-CI.UT`<-round(CI_UT[2],3)
  m$`num.LT-UT>0`<-sum(r$LTdep_AICw-r$UTdep_AICw>0,na.rm=T)
  m$`0.025-CI.Pl`<-round(rs$numericdf[5,3],3)
  m$`0.975-CI-Pl`<-round(rs$numericdf[5,4],3)
  m$`0.025-CI.Pu`<-round(rs$numericdf[6,3],3)
  m$`0.975-CI.Pu`<-round(rs$numericdf[6,4],3)
  m$`0.025-CI.Pl-Pu`<-round(rs$numericdf[10,3],3)
  m$`0.975-CI.Pl-Pu`<-list(round(rs$numericdf[10,4],3))
  #m$`CI0.975_Pl-Pu`<-round(rs$numericdf[10,4],3)
  #m$CI_Pl<-list(c(round(rs$numericdf[5,3],3),round(rs$numericdf[5,4],3)))
  #m$CI_Pu<-list(c(round(rs$numericdf[6,3],3),round(rs$numericdf[6,4],3)))
  #m$`CI_Pl-Pu`<-list(c(round(rs$numericdf[10,3],3),round(rs$numericdf[10,4],3)))

@@

d1<-data_aphid_count$`Green spruce aphid`[[4]]
d2<-data_aphid_count$`Green spruce aphid`[[11]]
pdf("./Results/Aphid_count_raw_loc_4_11.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 4.1, 0.2, 2.1))
plot(d1$Dat,d2$Dat,type="p",col="red",xlab="Green-spruce aphid count from location 4",ylab="Green-spruce aphid count from location 11",cex.lab=1.5,cex.axis=1.5)
par(op)
dev.off()

source("./vivj_matrix.R")
m<-vivj_matrix(d_allsp = data_aphid_count,sp=10,i=4,j=11)
pdf("./Results/Aphid_count_cop_loc_4_11.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 4.1, 0.2, 2.1))
plot(m[,1],m[,2],type="p",col="red",xlab="u",ylab="v",
     cex.lab=2,cex.axis=1.5,
     xlim=c(0,1),ylim=c(0,1),asp=1)
rect(0,0,1,1)
lines(c(0,1),c(0,1),type='l')
par(op)
dev.off()

# code to plot raw data and copula plot for aphid ff @location pair (2,5)
# bestfit cop : J
d1<-data_aphid_ff$`Leaf-curling plum aphid`[[2]]
d2<-data_aphid_ff$`Leaf-curling plum aphid`[[5]]
pdf("./Results/Aphid_ff_raw_loc_2_5.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 4.1, 0.2, 2.1))
plot(d1$Dat,d2$Dat,type="p",col="red",xlab="Leaf-plum curling aphid's first-flight from location 2",ylab="Leaf-plum curling aphid's first-flight from location 5",cex.lab=1.5,cex.axis=1.5)
par(op)
dev.off()

m<-vivj_matrix(d_allsp = data_aphid_ff,sp=11,i=2,j=5)
pdf("./Results/Aphid_ff_cop_loc_2_5.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 4.1, 0.2, 2.1))
plot(m[,1],m[,2],type="p",col="red",xlab="u",ylab="v",
     cex.lab=2,cex.axis=1.5,
     xlim=c(0,1),ylim=c(0,1),asp=1)
rect(0,0,1,1)
lines(c(0,1),c(0,1),type='l')
par(op)
dev.off()
```

@@

# Consequence of non-Normal copula structure : Effect on Taylor's law \label{Consequence_TL_simulation}

>>>>

---
title: "Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields"
author: "S. Ghosh, T. Loecke, C.P. Reid, D.C. Reuman"
date: "February 12, 2018"
geometry: "left=1cm,right=1cm,top=2.2cm,bottom=2.2cm"

@@

<!--The raw data look like this:-->
```{r load_data_Loecke, echo=F, results='hide'}
#fig.cap="Plot of the raw soil C and N data.\\label{fig_raw_cop_soilCN}(A)", fig.height=3, fig.width=3}
d<-readRDS("Data/RaCA_soilorganicC_soiltotalN_stocks100cm.RDS")
d<-d[,c("SOCstock100","TSNstock100")]
pdf("./Results/SoilCNraw.pdf")
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(d[,1],d[,2],type="p",col="red",xlab="Soil C",ylab="Soil N",cex.lab=2.5,cex.axis=1.5)
par(op)
dev.off()
```

@@

b<-log10(raw_b)
colnames(b)<-c("log10M(g)","log10BMR(KJ/h)")
pdf("./Results/BMR_results/birds/raw_birds_BMR.pdf")
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(b[,1],b[,2],type="p",col="red",xlab="log(Mass)",ylab="log(BMR)",cex.lab=2.5,cex.axis=1.5)
par(op)
dev.off()

@@

pdf("./Results/BMR_results/mammals/raw_mammals_BMR.pdf")
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(m[,1],m[,2],type="p",col="red",xlab="log(Mass)",ylab="log(BMR)",cex.lab=2.5,cex.axis=1.5)
par(op)
dev.off()

@@

  if(ploton==T){
    if(rawplot==T){
      op<-par(mar=c(5.1, 5.1, 1.5, 2.1))
      plot(tab_dbp$avg.H,tab_dbp$avg.Biomass,xlab="avg.H",ylab="avg.Biomass",col="red",pch=1,cex.lab=2.5,cex.axis=1.5)
      mtext(paste0("Year=",year),cex=2)
      par(op)
    }else{
      op<-par(mar=c(5.1, 5.1, 1.5, 2.1))
      plot(cop_tab_dbp$avg.H,cop_tab_dbp$avg.Biomass,xlab="u",ylab="v",col="red",pch=1,cex.lab=2.5,cex.axis=1.5,
         xlim=c(0,1),ylim=c(0,1),asp=1)
      rect(0,0,1,1)
      lines(c(0,1),c(0,1),type='l')
      mtext(paste0("Year=",year),cex=2)
      par(op)
    }
  }

@@

# Spatial resampling with multivariate datasets for non-parametric statistics \label{spatial_resamp}

The scheme is identical to that proposed by @bjornstadfalck2001 for application in their now 
widely used spline correlogram method; the same scheme was also used by @walteretal2017 
as part of a method for 
performing model selection among matrix regression models. For each pair of 
locations $i \neq j$, the statistic
of interest, here denoted $s_{ij}$ ($\cor_{l_b,u_b}$, $\Ps_{l_b,u_b}$, 
$\Dsq_{l_b,u_b}$, $\cor_l-\cor_u$, 
$\Ps_l-\Ps_u$, or $\Dsq_u-\Dsq_l$) was computed for those locations. The 
values $s_{ij}$ were then arranged in
a matrix, $S$, with diagonal entries NA. The mean of the non-NA entries of $S$ was computed. For 
$\cor_{l_b,u_b}$, $\Ps_{l_b,u_b}$, or $\Dsq_{l_b,u_b}$ this mean characterized the 
average strength of 
dependence, across all pairs of distinct locations, for data in the portion of the distributions 
given by $l_b$ and $u_b$. For $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, or $\Dsq_u-\Dsq_l$, the mean characterized average
asymmetry of tail dependence across all pairs of locations. 
Confidence intervals for the values of $\mean(S)$ were then computed as quantiles of a 
distribution of bootstrapped values. If $\mean(S)$ was significantly different from 0, as
revealed by these confidence intervals, for the statistics $\cor_l-\cor_u$, $\Ps_l-\Ps_u$, 
or $\Dsq_u-\Dsq_l$, then tail dependence was significantly asymmetric, in contrast to a 
Normal null hypothesis, and answering question \hyperref[MT-Intro]{\textbf{(Q1)}} from the \nameref{MT-Intro}.
Bootstrapping was performed by resampling the locations of measurement, with replacement. 
This corresponds to 
resampling, with replacement, the rows and columns of $S$, and is described in detail elsewhere 
[@bjornstadfalck2001 ; @walteretal2017].

# How to visualize non-parametric analysis results for multivariate spatial data? \label{visual_npa}

The principle remains same but for example we chose one of spatial data set (green spruce aphid's count) to illustrate results from Table \ref{tab_count_resamp}. Plotting Spearman or Kendall correlation between aphid abundance time series for pairs of locations as a function of great circle distance between the locations (Fig. \ref{fig_aphid_count} A,B) showed the typical decline of correlation with distance between sampling locations that has been seen for numerous other datasets in earlier work. Plotting $\cor_l$, $\cor_u$, $\Ps_l$, and $\Ps_u$  against distance between pairs of locations shows these quantities also decline with distance (Fig. \ref{fig_aphid_count} C-F). Plotting $\Dsq_u$ and  $\Dsq_l$ against distance between pairs of locations shows these quantities increase with distance (as expected, given the opposite interpretation these two statistics have compared to $\cor_u$, $\Ps_u$ and $\cor_l$, $\Ps_l$, respectively). Plotting $\cor_l - \cor_u$, $\Ps_l - \Ps_u$, and $\Dsq_u - \Dsq_l$ versus distance (Fig. \ref{fig_aphid_count} I-K) did not show a decline with distance, but did illustrate visually the statistical result of Table \ref{tab_count_resamp} that averages of these quantities across all pairs of sampling locations were significantly greater than zero, demonstrating asymmetry of tail dependence, as also seen from model selection approach. Code for these analyses is in [`NonParamStat.R`](https://github.com/sghosh89/BIVAN/blob/master/NonParamStat.R) in the [`BIVAN`](https://github.com/sghosh89/BIVAN) repository.

@@

<!--Display model selection results for BMR:birds data in a table-->
```{r tab_bmr_mammals_fit, echo=F, results='markup'}
h<-BivMS_mammals$InfCritRes[,c("copname","AICw","BICw","LTdep","UTdep")]
knitr::kable(h,
             format='pandoc',
             caption = "Fitting info for **mammals' BMR dataset** . \\label{tab_bmr_mammals_fit}",
             booktabs=T)
```

@@

\newpage
```{r tab_count_bestcop, echo=F, results="markup"}
#library(dplyr)
#knitr::opts_knit$set(kable.force.latex = TRUE)
knitr::kable(RES_aphid_count$info_ord_copname[,,1], #longtable = T,
             format='pandoc',
             #caption.short = "Best-fitting copulas for each location pair from among those considered, according to AIC, for abundances of the green spruce aphid.",
             caption = "Best-fitting copulas for each location pair from among those considered, according to AIC, for **abundances of the green spruce aphid**. Copulas 
considered were the normal, Clayton, Gumbel, Frank, Joe, BB1, BB6, BB7, BB8, survival Clayton, survival Gumbel, 
survival Joe, survival BB1, survival BB6, survival BB7, survival BB8 copulas. Abbreviations were given in \\nameref{MT-Methods}. NA occurs along the diagonal of the matrix because the diagonal represents a sampling location compared to itself.\\label{tab_count_bestcop}",
             booktabs=TRUE
             )#%>% # only with 'latex'/'html' format
 # kableExtra::kable_styling(latex_options = c("striped","HOLD_position"))
```

@@

```{r tab_count_AICw_normal, echo=F, results='markup'}
source("normal_cop_AICw.R")
knitr::kable(normal_cop_AICw_matrix(r=RES_aphid_count),
             format='pandoc',
             caption = "$\\text{AIC}_{\\text{w}}$ for the normal copula family for each location pair for **abundances of the green spruce aphid**, for comparison with Table \\ref{tab_count_AICw}. \\label{tab_count_AICw_normal}",
             booktabs=TRUE
             )
```

@@

\newpage
```{r tab_count_LTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_count$LTdep_AICw,
             format='pandoc',
             caption = "Model-averaged lower tail dependence statistic for each location pair for **abundances of the green spruce aphid**.\\label{tab_count_LTdep_AICw}",
             booktabs=TRUE
             )
```

\newpage
```{r tab_count_UTdep_AICw, echo=F, results='markup'}
knitr::kable(RES_aphid_count$UTdep_AICw,
             format='pandoc',
             caption = "Model averaged upper tail dependence statistic for each location pair for **abundances of the green spruce aphid**.\\label{tab_count_UTdep_AICw}",
             booktabs=TRUE
             )
```

\newpage
```{r tab_count_LTmUT, echo=F, results='markup'}
knitr::kable(RES_aphid_count$LTdep_AICw-RES_aphid_count$UTdep_AICw,
             digits = 5,
             format='pandoc',
             caption = "Model averaged lower tail dependence minus model averaged upper tail dependence statistic for each location pair for **abundances of the green spruce aphid**.\\label{tab_count_LTmUT}",
             booktabs=TRUE
             )
```

@@

\newpage
```{r tab_ff_AICw_normal, echo=F, results='markup'}
source("normal_cop_AICw.R")
knitr::kable(normal_cop_AICw_matrix(r=RES_aphid_ff),
             format='pandoc',
             caption = "$\\text{AIC}_{\\text{w}}$ for the normal copula family for each location pair for **first flight data for the leaf-curlung plum aphid**, for comparison with Table \\ref{tab_ff_AICw}.\\label{tab_ff_AICw_normal}",
             booktabs=TRUE
             )
```

@@

\newpage
<!--display the main statistical results in a table-->
```{r tab_methane_resamp,echo=F,results="markup"}
s<-stat_methane$numericdf[,c(3,2,4)]
colnames(s)<-c("Lower 95\\% CI", "Mean", "Upper 95\\% CI")
rownames(s)<-c("Spearman","Kendall","$\\cor_l$","$\\cor_u$","$\\Ps_l$","$\\Ps_u$","$\\Dsq_l$","$\\Dsq_u$","$\\cor_l - \\cor_u$","$\\Ps_l - \\Ps_u$","$\\Dsq_u - \\Dsq_l$")
knitr::kable(s,
             format = "pandoc",
             caption = "Spatially averaged values of statistics and confidence intervals based on resampling for **methane-flux data**.\\label{tab_methane_resamp}",
             booktabs=TRUE)
```

@@

  d<-dim(r$gfc_numBS)[1]
  m$num.pairs<-(d^2)-d 
  m$`num.non-indep`<- (d^2)-d-2*(r$num_indep_loc_pair+r$num_neg_cor_loc_pair)
  m$`num.non-N`<-sum(r$info_ord_copcode[,,1]!=1,na.rm = T)
  r$info_ord_AICw[r$info_ord_AICw==Inf] <- NaN
  m$Avg.best.AICw<-round(mean(r$info_ord_AICw[,,1],na.rm = T),3)
  normal_AICw[normal_AICw==Inf]<-NaN
  m$Avg.N.AICw<-round(mean(normal_AICw,na.rm=T),3)
  temp<-which((r$gfc_p_CvM>0.01) & (r$gfc_p_KS>0.01),arr.ind=T)
  m$num.good.fit<-dim(temp)[1]
  t<-r$LTdep_AICw[is.finite(r$LTdep_AICw)]
  CI_LT<-unname(quantile(t,probs=c(0.025,0.975),na.rm = T))
  m$`0.025-CI.LT`<-round(CI_LT[1],3)
  m$`0.975-CI.LT`<-round(CI_LT[2],3)
  t<-r$UTdep_AICw[is.finite(r$UTdep_AICw)]
  CI_UT<-unname(quantile(t,probs=c(0.025,0.975),na.rm = T))
  m$`0.025-CI.UT`<-round(CI_UT[1],3)
  m$`0.975-CI.UT`<-round(CI_UT[2],3)
  m$`num.LT-UT>0`<-sum(r$LTdep_AICw-r$UTdep_AICw>0,na.rm=T)
  m$`0.025-CI.Pl`<-round(rs$numericdf[5,3],3)
  m$`0.975-CI-Pl`<-round(rs$numericdf[5,4],3)
  m$`0.025-CI.Pu`<-round(rs$numericdf[6,3],3)
  m$`0.975-CI.Pu`<-round(rs$numericdf[6,4],3)
  m$`0.025-CI.Pl-Pu`<-round(rs$numericdf[10,3],3)
  m$`0.975-CI.Pl-Pu`<-list(round(rs$numericdf[10,4],3))
  #m$CI_Pl<-list(c(round(rs$numericdf[5,3],3),round(rs$numericdf[5,4],3)))
  #m$CI_Pu<-list(c(round(rs$numericdf[6,3],3),round(rs$numericdf[6,4],3)))
  #m$`CI_Pl-Pu`<-list(c(round(rs$numericdf[10,3],3),round(rs$numericdf[10,4],3)))

@@

d1<-data_aphid_count$`Green spruce aphid`[[4]]
d2<-data_aphid_count$`Green spruce aphid`[[11]]
pdf("./Results/Aphid_count_raw_loc_4_11.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(d1$Dat,d2$Dat,type="p",col="red",xlab="Green-spruce aphid count (loc. 4)",ylab="Green-spruce aphid count (loc. 11)",cex.lab=2.5,cex.axis=1.5)
par(op)
dev.off()

source("./vivj_matrix.R")
m<-vivj_matrix(d_allsp = data_aphid_count,sp=10,i=4,j=11)
pdf("./Results/Aphid_count_cop_loc_4_11.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(m[,1],m[,2],type="p",col="red",xlab="u",ylab="v",
     cex.lab=2.5,cex.axis=1.5,
     xlim=c(0,1),ylim=c(0,1),asp=1)
rect(0,0,1,1)
lines(c(0,1),c(0,1),type='l')
par(op)
dev.off()

# code to plot raw data and copula plot for aphid ff @location pair (2,5)
# bestfit cop : J
d1<-data_aphid_ff$`Leaf-curling plum aphid`[[2]]
d2<-data_aphid_ff$`Leaf-curling plum aphid`[[5]]
pdf("./Results/Aphid_ff_raw_loc_2_5.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(d1$Dat,d2$Dat,type="p",col="red",xlab="Leaf-plum curling's first-flight (loc. 2)",ylab="Leaf-plum curling's first-flight (loc. 5)",cex.lab=2.5,cex.axis=1.5)
par(op)
dev.off()

m<-vivj_matrix(d_allsp = data_aphid_ff,sp=11,i=2,j=5)
pdf("./Results/Aphid_ff_cop_loc_2_5.pdf",height = 8,width=8)
op<-par(mar=c(5.1, 5.1, 0.2, 2.1))
plot(m[,1],m[,2],type="p",col="red",xlab="u",ylab="v",
     cex.lab=2.5,cex.axis=1.5,
     xlim=c(0,1),ylim=c(0,1),asp=1)
rect(0,0,1,1)
lines(c(0,1),c(0,1),type='l')
par(op)
dev.off()
```

@@

\newpage
# Consequence of non-Normal copula structure : Effect on Taylor's law \label{Consequence_TL_simulation}
